---
title: "Projekt 1.2"
author: "Maciej Orsłowski"
date: '`r Sys.Date()`'
output: html_document
---

# Pakiet: arsenal
# Zadanie: regresja


```{r}
#tutaj ładuje wszystkie potrzebne biblioteki
library(arsenal)
library(dplyr)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview of functionalities

### Dataset

I am using the Sydney Houses dataset.

```{r}
path_to_data <- '../dataset_proj/datasets/sydney_house_prices_regression.csv'
df <- read.csv(path_to_data)
head(df, n = 10)
```

#### Compare datasets 

```{r}
summary(comparedf(head(df, n = 200), iris))
```

### Validity

#### Missing values

The library provides two functions related to missing values: `allNa` & 
`includeNA`. The former tests whether all values in a given vector are `NA`
while the latter replaces all `NA` values in a given vector with a 
specified value

```{r}
allNA(df)
allNA(c(NA, NA, NA))
allNA(c(NA, 1, NA))

vector_with_na <- c(10, 25, NA, 100, NA)
includeNA(vector_with_na, label = -1)
```

#### Atypical values 

A `freqlist` function can be useful for detecting duplicate rows or fragments
of rows in a dataframe. Since it counts how many times a certain combination
of variable values occurs in a dataframe it can also be used to identify
atypical values.
Note that it can get extremely slow when passingcharacter variables 
(it froze my laptop when I tried to pass an entire dataframe)

```{r}
tab <- table(df %>% select('bed', 'bath', 'car'))
frlist <- freqlist(tab)
head(summary(frlist))

frlist <- freqlist(~ bed + bath + car, data = df)
head(summary(frlist))
```

### Univar.

This package doesn't provide any tools related to this category.

### Bivar.


#### Time-dependency

The package provides a `paired` function which can compare observations taken
from two different time points. Since it requires a very specific data frame
format, I decided to manually add columns to the Sydney Houses data that are
necessary for the function to work. Note that these added columns do not make 
any logical sense in this data - their only purpose is to make `paired`
return any output

```{r}
df_with_time <- head(df, n = 1000)
df_with_time$time_point <- rep(c(1, 2), length.out = 1000)
df_with_time$id <- c(1:500, 500:1)
p <- paired(time_point ~ car + bath + bed + sellPrice, data = df_with_time, id = id, na.action = na.paired("fill"))
summary(p)
```

#### Contigency tables

A `tableby` function can generate contingency tables for two or more
variables. The first variable (one on the left of the formula) has to be a
categorical variable. Variables on the right side will be summarised in groups
defined by the first variable

```{r}
t <- tableby(propType ~ bed + suburb, data = head(df, 200))
summary(t)
```

### Multivar.  

#### Stat. models 

A `modelsum` function can be used to fit simple statistical models. It seems
to be a kind of merge of `lm` and `glm`.

The library also provides a function `formulize` that can generate formulas 
from vectors of variable names. 
It can be especially useful when generating formulas dynamically.

```{r}
y <- 'sellPrice'
x <- c('bed', 'car', 'bath')
modelsum(formulize(y, x), data = df)

# above code is equivalent to:
# modelsum(sellPrice ~ bed + car + bath, data = df)
```

### Reporting

#### Saving outputs        

The package comes with a `write2` function that can be used to output
tables to a HTML, PDF or a Word file. I couldn't get it to work though
(it would always generate an empty file without showing any errors)

```{r}
# output <- comparedf(head(df, 200), iris)
# write2html(output, 'file.html')
# write2pdf(output, 'file.pdf')
# write2word(output, 'file.doc')
```

## Summary

|  Task type | Task                  | Yes/No |
|:----------:|-----------------------|--------|
|   Dataset  | Variable types        |  No    |
|            | Dimensions            |  No    |
|            | Other info            |  No    |
|            | Compare datasets      |  Yes   |
|  Validity  | Missing values        |  Yes   |
|            | Redundant col.        |  No    |
|            | Outliers              |  No    |
|            | Atypical values       |  Yes   |
|            | Level encoding        |  No    |
|   Univar.  | Descriptive stat.     |  No    |
|            | Histograms            |  No    |
|            | Other dist. plots     |  No    |
|            | Bar plots             |  No    |
|            | QQ plots              |  No    |      
|   Bivar.   | Descriptive stat.     |  No    |       
|            | Correlation matrix    |  No    |
|            | 1 vs each corr.       |  No    |
|            | Time-dependency       |  Yes   |             
|            | Bar plots by target   |  No    |
|            | Num. plots by target  |  No    |
|            | Scatter plots         |  No    |
|            | Contigency tables     |  Yes   |
|            | Other stats. (factor) |  No    |
|  Multivar. | PCA                   |  No    |      
|            | Stat. models          |  Yes   |
|            | PCP                   |  No    |
| Transform. | Imputation            |  No    |
|            | Scaling               |  No    |
|            | Skewness              |  No    |
|            | Outlier treatment     |  No    |
|            | Binning               |  No    |
|            | Merging levels        |  No    |
|  Reporting | Reports               |  No    |
|            | Saving outputs        |  Yes   |  