---
title: "Projekt 1.2"
author: "Marcel Witas"
date: '`r Sys.Date()`'
output: html_document
---

# Pakiet: DataExplorer
# Zadanie: regresja


Package DataExplorer can help us with different tasks throughout your data exploration process.

There are 3 main goals for DataExplorer: Exploratory Data Analysis (EDA), Feature Engineering, Data Reporting.

```{r}
library(DataExplorer)
df <- read.csv("../dataset/KwiecinskiTymoteusz/regression.csv")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview of functionalities

### Dataset
I will use dataset about wine from github.
```{r}
print(head(df))
```

#### Variable types
By plot_str we visualize variables with types.
```{r}
plot_str(df)
```

#### Dimensions
By plot_str we visualize also dimensions.
```{r}
#plot_str(df)
```

#### Other info

```{r}
introduce(df)
```

We have info about: 
rows,	columns, discrete_columns, 	
continuous_columns, all_missing_columns	
total_missing_values,	complete_rows	
total_observations, memory_usage


#### Compare datasets
Not possible with DataExplorer
```{r}

```

### Validity

#### Missing values 
We can see plot with missing values in each column, or table with number and percentage of missing in each column.
```{r}
#to plot:
plot_missing(df)
#table with number and percentage of missing in each column:
profile_missing(df)
```

#### Redundant col.
Not possible with DataExplorer
```{r}

```

#### Outliers 
Not possible with DataExplorer
```{r}

```


#### Atypical values
Not possible with DataExplorer
```{r}

```


#### Level encoding 
Not possible with DataExplorer
```{r}

```

### Univar.

#### Descriptive stat.
Not possible with DataExplorer
```{r}

```

#### Histograms 
We can plot histograms of numerical variables.
```{r}
plot_histogram(df)
```

#### Other dist. plots
Not possible with DataExplorer
```{r}

```

#### Bar plots 
We can plot barplots of categorical variables.
```{r}
plot_bar(df)
```

#### QQ plots
QQ plots are provided, also by another feature.
```{r}
plot_qq(df$price)
```

### Bivar.     

#### Descriptive stat.
Not possible with DataExplorer
```{r}

```

#### Correlation matrix 
We can see correlation heatmap, and package handles categorical variables on correlation plots by creating dummy features.

```{r}
plot_correlation(na.omit(df), maxcat = 5L)
```

#### 1 vs each corr.   
Not possible with DataExplorer
```{r}

```

#### Time-dependency  
Not possible with DataExplorer
```{r}

```

#### Bar plots by target  

Argument "with" is name of continuous feature to be summed. But here we would prefer
mean of rating. There can also pass argument by.
```{r}
plot_bar(df, with = "Rating")
plot_bar(df, by = "is_natural")
```

#### Num. plots by target 
We may visualize the distribution of all continuous features based on target with a boxplot:
```{r}
plot_boxplot(na.omit(df), by = "Rating")
```

#### Scatter plots 
Scatterplots are also possible. 
```{r}
plot_scatterplot(df, by = "Rating", sampled_rows = 1000L)
```

#### Contigency tables   
Not possible with DataExplorer
```{r}

```

#### Other stats. (factor)
Not possible with DataExplorer
```{r}

```


### Multivar.  

#### PCA 
To perform and visualize PCA:

```{r}
plot_prcomp(na.omit(df) )
```

#### Stat. models  
Not possible with DataExplorer
```{r}

```

#### PCP        
Not possible with DataExplorer
```{r}

```


### Transform. 

#### Imputation

If you specify a number, all missing continuous values will be set to that number. If you specify a string, all missing discrete values will be set to that string. If you supply both, both types will be set.

```{r}
df2 <- set_missing(df, list(0L, "unknown"))
```

#### Scaling 
Not possible with DataExplorer
```{r}

```

#### Skewness   
Not possible with DataExplorer
```{r}

```

#### Outlier treatment  
Not possible with DataExplorer
```{r}

```

#### Binning  
Binning is possible indirectly, fuction update_columns can do it after defining function making bins. For example:

```{r}
bin_price <- function(x) cut(x, breaks = c(0L, 30L, 60L, 90L, 120L, 500L))
transformed_data <- update_columns(df, "price", bin_price)

plot_bar(transformed_data$price)
```

#### Merging levels     
Group bottom "threshold" (by count) to "OTHER" category.
```{r}
df3 <- group_category(data = df, feature = "Country", threshold = 0.2, update = TRUE)
```

### Reporting  

#### Reports
There is function to generate report, where we can pass target variable.

```{r}
#create_report(df, y = "Rating")
```

You may also customize each individual section using configure_report function.

#### Saving outputs        
Not possible with DataExplorer
```{r}

```



## Summary

|  Task type | Task                  | Yes/No |
|:----------:|-----------------------|--------|
|   Dataset  | Variable types        | Yes    |
|            | Dimensions            | Yes    |
|            | Other info            | Yes    |
|            | Compare datasets      | No     |
|  Validity  | Missing values        | Yes    |
|            | Redundant col.        | No     |
|            | Outliers              | No     |
|            | Atypical values       | No     |
|            | Level encoding        | No     |
|   Univar.  | Descriptive stat.     | No     |
|            | Histograms            | Yes    |
|            | Other dist. plots     | No     |
|            | Bar plots             | Yes    |
|            | QQ plots              | Yes    |    
|   Bivar.   | Descriptive stat.     | No     |       
|            | Correlation matrix    | Yes    |
|            | 1 vs each corr.       | No     |
|            | Time-dependency       | No     |             
|            | Bar plots by target   | Yes    |
|            | Num. plots by target  | Yes    |
|            | Scatter plots         | Yes    |
|            | Contigency tables     | No     |
|            | Other stats. (factor) | No     |
|  Multivar. | PCA                   | Yes    |      
|            | Stat. models          | No     |
|            | PCP                   | No     |
| Transform. | Imputation            | Yes    |
|            | Scaling               | No     |
|            | Skewness              | No     |
|            | Outlier treatment     | No     |
|            | Binning               | Yes    |
|            | Merging levels        | Yes    |
|  Reporting | Reports               | Yes    |
|            | Saving outputs        | No     |  
