---
title: "Projekt 1.2"
author: "Antoni Chudy"
date: '`r Sys.Date()`'
output: html_document
---

# Pakiet: DataExplorer
# Zadanie: klasyfikacja


```{r}
library(DataExplorer)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview of functionalities

### Dataset

```{r}

df <- iris
```

#### Variable types

```{r}
plot_str(df)
```

#### Dimensions

```{r}
introduce(df)
```

#### Other info

```{r}
plot_intro(df)
```

#### Compare datasets

```{r}
```

### Validity

#### Missing values 

```{r}
plot_missing(df)
profile_missing(df)
```

#### Redundant col.

```{r}

```

#### Outliers 

```{r}
```


#### Atypical values

```{r}
```


#### Level encoding 

```{r}
dummify(df)
```

### Univar.

#### Descriptive stat.

```{r}
```

#### Histograms 

```{r}
plot_histogram(df)
```

#### Other dist. plots

```{r}
plot_density(df)
```

#### Bar plots 

```{r}
plot_bar(df)
```

#### QQ plots

```{r}
plot_qq(df$Sepal.Length)
```

### Bivar.     

#### Descriptive stat.

```{r}
```

#### Correlation matrix 

```{r}
plot_correlation(na.omit(df), maxcat = 5L)
```

#### 1 vs each corr.   

```{r}
```

#### Time-dependency  

```{r}
```

#### Bar plots by target  

```{r}
plot_bar(df, with = "Sepal.Width")
```

#### Num. plots by target 

```{r}
plot_boxplot(na.omit(df), by = "Sepal.Width")
```

#### Scatter plots 

```{r}
plot_scatterplot(df, by = 'Sepal.Length')
```

#### Contigency tables   

```{r}
```

#### Other stats. (factor)

```{r}
```


### Multivar.  

#### PCA 

```{r}
plot_prcomp(na.omit(df), variance_cap = 0.9, nrow = 2L, ncol = 2L)
```

#### Stat. models  

```{r}
```

#### PCP        

```{r}
```


### Transform. 

#### Imputation

```{r}
set_missing(df, list(0L, "unknown"))
```

#### Scaling 

```{r}
```

#### Skewness   

```{r}
```

#### Outlier treatment  

```{r}
```

#### Binning  

```{r}

```

#### Merging levels     

```{r}

group_category(data = df, feature = "Sepal.Length", threshold = 0.1, update = TRUE)

```

### Reporting  

#### Reports

```{r}
create_report(df)
```

#### Saving outputs        

```{r}
```



## Summary

|  Task type | Task                  | Yes/No |
|:----------:|-----------------------|--------|
|   Dataset  | Variable types        |   Yes  |
|            | Dimensions            |   Yes  |
|            | Other info            |   Yes  |
|            | Compare datasets      |   No   |
|  Validity  | Missing values        |   Yes  |
|            | Redundant col.        |   No   |
|            | Outliers              |   No   |
|            | Atypical values       |   No   |
|            | Level encoding        |   Yes  |
|   Univar.  | Descriptive stat.     |   No   |
|            | Histograms            |   Yes  |
|            | Other dist. plots     |   Yes  |
|            | Bar plots             |   Yes  |
|            | QQ plots              |   Yes  |      
|   Bivar.   | Descriptive stat.     |   No   |       
|            | Correlation matrix    |   Yes  |
|            | 1 vs each corr.       |   No   |
|            | Time-dependency       |   No   |             
|            | Bar plots by target   |   Yes  |
|            | Num. plots by target  |   Yes  |
|            | Scatter plots         |   Yes  |
|            | Contigency tables     |   No   |
|            | Other stats. (factor) |   No   |
|  Multivar. | PCA                   |   Yes  |      
|            | Stat. models          |   No   |
|            | PCP                   |   No   |
| Transform. | Imputation            |   Yes  |
|            | Scaling               |   No   |
|            | Skewness              |   No   |
|            | Outlier treatment     |   No   |
|            | Binning               |   No   |
|            | Merging levels        |   Yes  |
|  Reporting | Reports               |   Yes  |
|            | Saving outputs        |   No   |  