
---
title: "Projekt 1.2"
author: "Mateusz Madej"
date: '`r Sys.Date()`'
output: html_document
---
  
  # Pakiet: dlookr
  # Zadanie: regresja
  
  
```{r}
#tutaj ładuje wszystkie potrzebne biblioteki
#library()
library(dlookr)
library(dplyr)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Overview of functionalities

### Dataset

```{r}
# Regresja
n <- 500
# Niezr?wnowazone klasy
y <- sample(0:1, size=n, replace=TRUE, prob = c(0.3,0.7))
y1 <- sum(y==1)
y0 <- n-y1
# Nieskorelowana zmienna
x0 <- rnorm(n,3,5) + rgamma(n,1,1)
# Przycieta zmienna
x1 <- numeric(n)
x1[y==0] <- 3 + rnorm(y0,0,2)
x1[y==1] <- 5 + rnorm(y1, 0, 3)
x1[x1>=6.25] <- 6.25
x1[x1<=1.75] <- 1.75
# NULL i dyskretna
x2 <- numeric(n)
prob0 <- c(0.35, 0.30, 0.20, 0.15)
prob1 <- c(0.20, 0.10, 0.40, 0.30)
x2[y==0] <- sample(1:4,y0, replace=TRUE, prob=prob0)
x2[y==1] <- sample(1:4,y1, replace=TRUE, prob=prob1)
x2_NULL <- rbinom(n,1,prob=0.05)
x2[x2_NULL==1] <- NaN
# W pelni objasnia y
x3 <- numeric(n)
x3[y==0] <- 1.32
x3[y==1] <- 5.64
# Dwie mocno skorelowane
x4 <- numeric(n)
x4[y==0] <- rbeta(y0,3,1) 
x4[y==1] <- rbeta(y1,1,3)

x5 <- numeric(n)
x5 <- x4 + + rnorm(n, 0, 0.25)

dataRegression <- data.frame(x0,x1,x2,x3,x4,x5,y)
dataRegression
```

#### Variable types

```{r}
diagnose(dataRegression)
```

#### Dimensions

```{r}
describe(dataRegression)
```

#### Other info

```{r}
diagnose(dataRegression)
```

#### Compare datasets

```{r}
```

### Validity

#### Missing values 

```{r}
describe(dataRegression)
diagnose(dataRegression)
```

#### Redundant col.

```{r}
correlate(dataRegression)
plot_correlate(dataRegression)
```

#### Outliers 

```{r}
describe(dataRegression)
plot_outlier(dataRegression)
diagnose_outlier(dataRegression)
```


#### Atypical values

```{r}
```


#### Level encoding 

```{r}
```

### Univar.

#### Descriptive stat.

```{r}
diagnose(dataRegression)
```

#### Histograms 

```{r}
plot_hist_numeric(dataRegression)
```

#### Other dist. plots

```{r}
```

#### Bar plots 

```{r}
plot_bar_category(dataRegression)
```

#### QQ plots

```{r}
plot_normality(dataRegression)
```

### Bivar.     

#### Descriptive stat.

```{r}
describe(dataRegression)
```

#### Correlation matrix 

```{r}
dataRegression %>% 
plot_correlate(x1, x2)
```

#### 1 vs each corr.   

```{r}
dataRegression %>% 
  correlate(x1)
```

#### Time-dependency  

```{r}
```

#### Bar plots by target  

```{r}
```

#### Num. plots by target 

```{r}
```

#### Scatter plots 

```{r}
by <- target_by(dataRegression, y)
m1 <- relate(by, x4)
plot(m1, 1)
```

#### Contigency tables   

```{r}
```

#### Other stats. (factor)

```{r}
```


### Multivar.  

#### PCA 

```{r}
```

#### Stat. models  

```{r}
by <- target_by(dataRegression, y)
m1 <- relate(by, x4)
plot(m1, 1)
```

#### PCP        

```{r}
```


### Transform. 

#### Imputation

```{r}
imputate_na(dataRegression, x2)
imputate_outlier(dataRegression, x5)
```

#### Scaling 

```{r}
```

#### Skewness   

```{r}
skewness(dataRegression$x1)
```

#### Outlier treatment  

```{r}
diagnose_outlier(dataRegression)
imputate_outlier(dataRegression, x0)
```

#### Binning  

```{r}
binning(dataRegression$x1)
```

#### Merging levels     

```{r}
```

### Reporting  

#### Reports

```{r}
#diagnose_web_report(dataRegression)
#eda_web_report(dataRegression)
```

#### Saving outputs        

```{r}
```



## Summary

|  Task type | Task                  | Yes/No |
  |:----------:|-----------------------|--------|
  |   Dataset  | Variable types        | Yes    |
  |            | Dimensions            | Yes    |
  |            | Other info            | Yes    |
  |            | Compare datasets      | No     |
  |  Validity  | Missing values        | Yes    |
  |            | Redundant col.        | Yes    |
  |            | Outliers              | Yes    |
  |            | Atypical values       | No     |
  |            | Level encoding        | No     |
  |   Univar.  | Descriptive stat.     | Yes    |
  |            | Histograms            | Yes    |
  |            | Other dist. plots     | No     |
  |            | Bar plots             | Yes    |
  |            | QQ plots              | Yes    |      
  |   Bivar.   | Descriptive stat.     | Yes    |       
  |            | Correlation matrix    | Yes    |
  |            | 1 vs each corr.       | Yes    |
  |            | Time-dependency       | No     |             
  |            | Bar plots by target   | No     |
  |            | Num. plots by target  | No     |
  |            | Scatter plots         | Yes    |
  |            | Contigency tables     | No     |
  |            | Other stats. (factor) | Yes    |
  |  Multivar. | PCA                   | No     |      
  |            | Stat. models          | Yes    |
  |            | PCP                   | No     |
  | Transform. | Imputation            | Yes    |
  |            | Scaling               | No     |
  |            | Skewness              | Yes    |
  |            | Outlier treatment     | Yes    |
  |            | Binning               | Yes    |
  |            | Merging levels        | No     |
  |  Reporting | Reports               | Yes    |
  |            | Saving outputs        | No     |  