---
title: "Projekt 1.2"
author: "Paweł Drągowski"
date: '`12.04.2023`'
output: html_document
---

# Pakiet: ExPanDaR
# Zadanie: regresja

```{r}
#tutaj ładuje wszystkie potrzebne biblioteki
  
  library(ExPanDaR)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
dane <- read.csv('CarSeats.csv')
dane <- dane[,-1]
```

## Overview of functionalities

### Dataset

```{r}
```

#### Variable types

```{r}
```

#### Dimensions

```{r}
```

#### Other info

```{r}
```

#### Compare datasets

```{r}
```

### Validity

#### Missing values 

```{r}
prepare_missing_values_graph(dane,ts_id = "ShelveLoc")
```

#### Redundant col.

```{r}
```

#### Outliers 
```{r}
prepare_ext_obs_table(dane)
```


#### Atypical values

```{r}
```


#### Level encoding 

```{r}
```

### Univar.

#### Descriptive stat.

```{r}
prepare_descriptive_table(as.data.frame(dane$Sales))
```

#### Histograms 

```{r}
```

#### Other dist. plots

```{r}
```

#### Bar plots 

```{r}
```

#### QQ plots

```{r}
  prepare_quantile_trend_graph(dane,ts_id="Sales")
```

### Bivar.     

#### Descriptive stat.

```{r}
prepare_descriptive_table(dane[,2:3])
```

#### Correlation matrix 

```{r}
prepare_correlation_table(dane)
  prepare_correlation_graph(dane)
```

#### 1 vs each corr.   

```{r}
```

#### Time-dependency  

```{r}
```

#### Bar plots by target  

```{r}
```

#### Num. plots by target 

```{r}
```

#### Scatter plots 

```{r}
  prepare_scatter_plot(dane,"Sales","CompPrice")
```

#### Contigency tables   

```{r}
```

#### Other stats. (factor)

```{r}
prepare_trend_graph(dane,ts_id='Sales')
```


### Multivar.  

#### PCA 

```{r}
```

#### Stat. models  

```{r}
```

#### PCP        

```{r}
```


### Transform. 

#### Imputation

```{r}
```

#### Scaling 

```{r}
```

#### Skewness   

```{r}
```

#### Outlier treatment  

```{r}
treat_outliers(dane,percentile = 0.01)
```

#### Binning  

```{r}
```

#### Merging levels     

```{r}
```

### Reporting  

#### Reports

```{r}
```

#### Saving outputs        

```{r}
```



## Summary

|  Task type | Task                  | Yes/No |
|:----------:|-----------------------|--------|
|   Dataset  | Variable types        |  NO    |
|            | Dimensions            |  NO    |
|            | Other info            |  NO    |
|            | Compare datasets      |  NO    |
|  Validity  | Missing values        |  YES   |
|            | Redundant col.        |  NO    |
|            | Outliers              |  YES   |
|            | Atypical values       |  NO    |
|            | Level encoding        |  NO    |
|   Univar.  | Descriptive stat.     |  YES   |
|            | Histograms            |  NO    |
|            | Other dist. plots     |  NO    |
|            | Bar plots             |  NO    |
|            | QQ plots              |  NO    |      
|   Bivar.   | Descriptive stat.     |  YES   |    
|            | Correlation matrix    |  YES   |
|            | 1 vs each corr.       |  NO    |
|            | Time-dependency       |  NO    |             
|            | Bar plots by target   |  NO    |
|            | Num. plots by target  |  NO    |
|            | Scatter plots         |  YES   |
|            | Contigency tables     |  NO    |
|            | Other stats. (factor) |  YES   |
|  Multivar. | PCA                   |  NO    |      
|            | Stat. models          |  NO    |
|            | PCP                   |  NO    |
| Transform. | Imputation            |  NO    |
|            | Scaling               |  NO    |
|            | Skewness              |  NO    |
|            | Outlier treatment     |  YES   |
|            | Binning               |  NO    |
|            | Merging levels        |  NO    |
|  Reporting | Reports               |  NO    |
|            | Saving outputs        |  NO    |  
