---
title: "Projekt 1.2"
author: "Zuzanna Glinka"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

# Pakiet: ExPanDaR
# Zadanie: klasyfikacja


```{r}
#tutaj ładuje wszystkie potrzebne biblioteki
library(ExPanDaR)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview of functionalities

### Dataset

```{r}
df<-read.csv('/Users/zuzannaglinka/Downloads/train.csv')
```

#### Variable types

```{r}

```

#### Dimensions

```{r}
#
```

#### Other info

```{r}
```

#### Compare datasets

```{r}
```

### Validity

#### Missing values 

```{r}
prepare_missing_values_graph(df, 'Style')
```

#### Redundant col.

```{r}
```

#### Outliers 

```{r}
treat_outliers(df)
```


#### Atypical values

```{r}
```


#### Level encoding 

```{r}
```

### Univar.

#### Descriptive stat.

```{r}
prepare_descriptive_table(df)
ExPanD(df, components = c(descriptive_table = TRUE))
```

#### Histograms 

```{r}
ExPanD(df, components = c(histogram = TRUE))
```

#### Other dist. plots

```{r}
ExPanD(df, components = c(sample_selection = TRUE, subset_factor = TRUE, grouping = TRUE,
                           missing_values = TRUE, udvars = TRUE, ext_obs = TRUE, by_group_bar_graph = TRUE, by_group_violin_graph = TRUE, trend_graph = TRUE, quantile_trend_graph = TRUE, by_group_trend_graph = TRUE))
```

#### Bar plots 

```{r}
ExPanD(df, components = c(bar_chart = TRUE))
```

#### QQ plots

```{r}
```

### Bivar.     

#### Descriptive stat.

```{r}
```

#### Correlation matrix 

```{r}
ExPanD(df, components = c(corplot = TRUE))
```

#### 1 vs each corr.   

```{r}
```

#### Time-dependency  

```{r}
prepare_trend_graph(df, 'colName')
```

#### Bar plots by target  

```{r}
prepare_by_group_bar_graph(df, 'Style', 'Body')
ExPanD(df, components = c(bar_chart = TRUE)) 
```

#### Num. plots by target 

```{r}
prepare_by_group_trend_graph(df, 'Fruits', 'Style', 'Body')
ExPanD(df, components = c(trend_graph = TRUE)) 
```

#### Scatter plots 

```{r}
ExPanD(df, components = c(scatter_plot = TRUE)) 
```

#### Contigency tables   

```{r}
```

#### Other stats. (factor)

```{r}
```


### Multivar.  

#### PCA 

```{r}
```

#### Stat. models  

```{r}
#
```

#### PCP        

```{r}
```


### Transform. 

#### Imputation

```{r}
```

#### Scaling 

```{r}
```

#### Skewness   

```{r}
```

#### Outlier treatment  

```{r}
treat_outliers(df, 'Body')
```

#### Binning  

```{r}
```

#### Merging levels     

```{r}
```

### Reporting  

#### Reports

```{r}
```

#### Saving outputs        

```{r}
```



## Summary

|  Task type | Task                  | Yes/No |
|:----------:|-----------------------|--------|
|   Dataset  | Variable types        |   No   |
|            | Dimensions            |   Yes  |
|            | Other info            |   No   |
|            | Compare datasets      |   No   |
|  Validity  | Missing values        |   Yes  |
|            | Redundant col.        |   No   |
|            | Outliers              |  Yes   |
|            | Atypical values       |   No      |
|            | Level encoding        |   No    |
|   Univar.  | Descriptive stat.     |   Yes     |
|            | Histograms            |   Yes      |
|            | Other dist. plots     |   Yes      |
|            | Bar plots             |    Yes    |
|            | QQ plots              |   No      |      
|   Bivar.   | Descriptive stat.     |    No    |       
|            | Correlation matrix    |    Yes    |
|            | 1 vs each corr.       |    No    |
|            | Time-dependency       |    Yes    |             
|            | Bar plots by target   |    Yes    |
|            | Num. plots by target  |    Yes    |
|            | Scatter plots         |    Yes    |
|            | Contigency tables     |    No    |
|            | Other stats. (factor) |    No    |
|  Multivar. | PCA                   |   No     |      
|            | Stat. models          |  Yes      |
|            | PCP                   |    No    |
| Transform. | Imputation            |    No    |
|            | Scaling               |    No    |
|            | Skewness              |    No    |
|            | Outlier treatment     |    Yes    |
|            | Binning               |    no    |
|            | Merging levels        |    No    |
|  Reporting | Reports               |    No    |
|            | Saving outputs        |    No    |  
