---
title: "Projekt 1.2"
author: "Dominik Kędzierski"
date: '`r Sys.Date()`'
output: html_document
---

# Pakiet: Explore
# Zadanie: klasyfikacja


```{r}
library(explore)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview of functionalities

### Dataset

```{r}
df <- read.csv("star_6class.csv")
library(tidyr)
```

#### Variable types

```{r}
describe(df)
```

#### Dimensions

```{r}
explore(df)
```

#### Other info

```{r}
explore(df)
```

#### Compare datasets

```{r}

```

### Validity

#### Missing values 

```{r}
describe(df)
```

#### Redundant col.

```{r}

```

#### Outliers 

```{r}
explore(df)
```


#### Atypical values

```{r}

```


#### Level encoding 

```{r}

```

### Univar.

#### Descriptive stat.

```{r}
explore(df)
```

#### Histograms 

```{r}
explore(df)
```

#### Other dist. plots

```{r}
explore(df)

```

#### Bar plots 

```{r}
explore(df)
```

#### QQ plots

```{r}

```

### Bivar.     

#### Descriptive stat.

```{r}

```

#### Correlation matrix 

```{r}

```

#### 1 vs each corr.   

```{r}

```

#### Time-dependency  

```{r}

```

#### Bar plots by target  

```{r}
explore(df)
```

#### Num. plots by target 

```{r}
explore(df)
```

#### Scatter plots 

```{r}
explore(df)
```

#### Contigency tables   

```{r}

```

#### Other stats. (factor)

```{r}
explore(df, var=Star.type, var2 = Star.color)
```
Teoretycznie według dokumnetacji daje to korelacje aczkolwiek nie wygląda to jak korelacja, jest to korelacja pomiędzy tylko dwiema zmiennymi

### Multivar.  

#### PCA 

```{r}

```

#### Stat. models  

```{r}
explore(df)
```

#### PCP        

```{r}

```


### Transform. 

#### Imputation

```{r}

```

#### Scaling 

```{r}

```

#### Skewness   

```{r}

```

#### Outlier treatment  

```{r}

```

#### Binning  

```{r}

```

#### Merging levels     

```{r}

```

### Reporting  

#### Reports

```{r}
explore(df)
```

#### Saving outputs        

```{r}
report(df, output_dir = tempdir())
```



## Summary

|  Task type | Task                  | Yes/No |
|:----------:|-----------------------|--------|
|   Dataset  | Variable types        |   Yes  |
|            | Dimensions            |   Yes  |
|            | Other info            |   Yes  |
|            | Compare datasets      |   No   |
|  Validity  | Missing values        |   Yes  |
|            | Redundant col.        |   No   |
|            | Outliers              |   Yes  |
|            | Atypical values       |   No   |
|            | Level encoding        |   No   |
|   Univar.  | Descriptive stat.     |   Yes  |
|            | Histograms            |   Yes  |
|            | Other dist. plots     |   Yes  |
|            | Bar plots             |   Yes  |
|            | QQ plots              |   No   |      
|   Bivar.   | Descriptive stat.     |   No   |       
|            | Correlation matrix    |   No   |
|            | 1 vs each corr.       |   No   |
|            | Time-dependency       |   No   |             
|            | Bar plots by target   |   Yes  |
|            | Num. plots by target  |   Yes  |
|            | Scatter plots         |   Yes  |
|            | Contigency tables     |   No   |
|            | Other stats. (factor) | Yes/No |
|  Multivar. | PCA                   |   No   |      
|            | Stat. models          |   Yes  |
|            | PCP                   |   No   |
| Transform. | Imputation            |   No   |
|            | Scaling               |   No   |
|            | Skewness              |   No   |
|            | Outlier treatment     |   No   |
|            | Binning               |   No   |
|            | Merging levels        |   No   |
|  Reporting | Reports               |   Yes  |
|            | Saving outputs        |   Yes  |  