---
title: "Projekt 1.2"
author: "Tymoteusz Kwieciński"
date: '`r Sys.Date()`'
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

# Pakiet: funModeling

# Zadanie: regression

## Description

The package should cover most of the topics connected to exploratory
data analysis, data preparation, and model performance. It is connected
to the *Live Book* <https://livebook.datascienceheroes.com/>, and those
two elements are meant to be sufficient tools for the mentioned topics.

However, as it turns out, the package and the book are not the best
solutions to those problems, yet they still contain interesting
functions and some introduction to Exploratory Data Analysis.

```{r}
library(funModeling)
library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)
#load libraries and my file
wine_data <- read.csv("../dataset/KwiecinskiTymoteusz/regression.csv")

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview of functionalities

### Dataset

The library provides a dataset about some heart diseases. It contains
some data about patients and their symptoms. The final column describes
whether a patient suffers from heart disease or not.

Additionally, it contains some smaller datasets with fewer features
and/or observations - but each of them should be more naturally used as
a dataset with a categorical target.

Therefore, to present the library's capabilities, I will use a different
column as a target feature.

The dataset comes from:
<https://archive.ics.uci.edu/ml/datasets/Heart+Disease>

Unfortunately, we cannot use this dataset since it is not meant for
regression. That is why I will use a different dataframe that I scraped
from the *Vivino* website. On this website, you can find ratings of many
other wines worldwide. The target feature in the given dataset is the
column `Rating`, an average of users' rates for the specified wine.

```{r}
print(head(wine_data))

```

#### Variable types

```{r}
status(wine_data)
```

The function provides insight not only into the types of variables but
also gives information about missing data and the number of unique
values. Everything is summarised in a tidy output describing the
properties of each feature.

The `wine_data` dataset contains 17 features, including target -
`Rating`. There exist some values that need to be added, although the
majority of data is present.

The summary allows us to easily identify columns with many `NA` values,
for instance, `sweetness` or ID-like ones - `X`. Even though intuition
tells otherwise `Wine.ID` and `Wine` might not necessarily be all
unique - $\frac{1}{3}$ of the values are unrepeatable.

#### Dimensions

not sure if there exists any function that provides the desired output,
but we can use the usual `dim` function.

```{r}
dim(wine_data)

```

The dataframe contains a relatively small number of observations.

#### Other info

```{r}
di=data_integrity(wine_data)

# returns a summary
summary(di)

```

Function data_integrity combined with the summary function returns a
handy and compressed output containing information on which columns
contain NA values and which features have greater cardinality. The
output simply contains columns that need some closer examination.

Function data_integrity returns an 'integrity' object; it contains much
more insight about the columns in the specified types.

The output suggests which columns we should investigate more. Variable
`has_valid_ratings` should probably be dropped as it has only one value.
There are some columns with high cardinality and numerical variables
with `NA` values.

```{r}
print(di)

```

Full description retrieved from the `data_integrity` function provides
information about all types of columns.

Some variables could be converted into different formats. For instance -
column `Year` is denoted as a `character` value, yet it is obviously a
number.

#### Compare datasets

```{r}

a=wine_data
b=wine_data
a=subset(a, num_review > 45)
b=subset(b, num_review < 50)

res=compare_df(a, b, c('Wine', 'num_review', 'Year'))
# Print the keys that didn't match
# Accessing the keys not present in the first data frame
head(res$rows_not_in_X)
# Accessing the keys not present in the second data frame
head(res$rows_not_in_Y)
# Accessing the keys which coincide completely
head(res$coincident)
# Accessing the rows whose values did not coincide
# res$different_values - provided in the description although not present in the package
```

Function describes the different kinds of observations in the compared
dataframes. Returns a list with 3 elements containing observations that
are common for both dataframes and which are present in the first, or
the second one. The comparison is made based on the given key column
names or simply every feature in the observations.

It is noticeable that there are multiple wines with the same name or ID
number but different `Year`. It probably means that the user rating
depends on the production year of the wine.

### Validity

#### Missing values

```{r}
status(wine_data)
```

Described above in the section about variable types.

#### Redundant col.

```{r}
print(":(")
```

One could say that the function `compare_df` or `v_compare` could be
used to detect redundant columns, but these only take two vectors and
execute comparisons between them. The package doesn't provide any
sensible solution to this problem.

#### Outliers

```{r}

tukey_outlier(wine_data$num_review)

```

The function `tukey_outlier` calculates the outlier threshold using the
Inter-quartile range.

```{r}

hampel_outlier(wine_data$num_review, k_mad_value = 3)

```

This more complicated function calculates a threshold outside which
outliers could be placed. `NA` values are automatically excluded. Uses
the *Hampel* algorithm. More information about:
<https://livebook.datascienceheroes.com/data-preparation.html#how_to_deal_with_outliers_in_r>

Unfortunately doesn't work for categorical variables (doesn't flag
variables with high cardinality).

#### Atypical values

```{r}
print(":(")
```

As far as I know, the package doesn't provide any other atypical values
detection.

However, function `freq` may be used to solve the problem of high
cardinality, as it can be used to remove categories with small number of
observations:

```{r}
country_freq <- freq(wine_data, 'Country', plot = F)

# country_freq is ordered by frequency
country_freq[1:3,]
countries <- country_freq[1:3, "Country"]

limited_countries_df = wine_data %>% mutate(Country = ifelse(Country %in% countries, Country, 'Other'))

freq(limited_countries_df, "Country")
```

Ordering the unique values by frequency is quite handy; it allows us to
eliminate the remaining, probably less informative categories.

More about it in the bar plot category.

#### Level encoding

```{r}
print(":(")
```

The package `funModeling` doesn't provide a solution to this problem,
although it is recommended by the autors to use the package `caret`,
which provides a thriving way to encode categorical values.

### Univar.

#### Descriptive stat.

```{r}
profiling_num(wine_data)
```

Gives a detailed desctiption of numerical variables. Output is much more
detailed than the one from basic functions.

Calculates skewness, percentiles and many other standard statistical
measures.

Works well with *pipe* - the output can be grouped and modified for
instance by `dplyr` package.

What could be done better in the given function is the clarity of the
output - in the given example there are many numbers written in the
scientific notation, which makes it difficult to quickly skim through
the numbers.

#### Histograms

```{r}
wine_data %>% plot_num(bins = 30)
```

A beautiful function that plots everything that we need - it has an
option of using a different number of bins, as well as is capable of
exporting the output into the file.

#### Other dist. plots

```{r}
print(":(")
```

#### Bar plots

```{r}
limited_countries_df %>% select(Country, Year, Rating, price) %>% freq()

```

Function `freq` calculates the frequency of the categorical variables.
It creates a summary dataframe for each of the non-numerical columns and
then has the option to plot them aesthetically.

What is a minus? Function parameters are not adjustable - it is
prohibited to plot variables with more than `100` categories, and it can
generate an enormous output, which is difficult to handle.

#### QQ plots

```{r}
print(":(")

#qqnorm(wine_data$Rating)
```

### Bivar.

#### Descriptive stat.

```{r}
numeric_wine_data <- select_if(wine_data, is.numeric) 

var_rank_info(numeric_wine_data, "Rating")
```

The function calculates several metrics related to information theory
between columns and a given target. The calculated metrics are entropy
(en), mutual information (mi), information gain (ig) and gain ratio
(gr). Variable names are ordered by gain ratio metric.

```{r}
infor_magic(wine_data$price, wine_data$Rating)

```

There are some other functions calculating the same metrics but for a
two vectors, or for simply evaluating the chosen metric only.

```{r}
information_gain(wine_data$price, wine_data$Rating)
```

#### Correlation matrix

```{r}
print(":(")
```

#### 1 vs each corr.

```{r}
correlation_table(wine_data, 'Rating')
```

The function calculates a correlation table (Pearson coefficient) for
all numerical columns compared to the given target column (if target
column isn't numerical, it will be converted to one).

Lacks different correlation coefficients.

#### Time-dependency

```{r}
print(":(")
```

#### Bar plots by target

```{r}
cross_plot(limited_countries_df, input="Country", target="is_natural")
```

Target has to be categorical in this case. Not very useful in our
regression case.

#### Num. plots by target

```{r}
di <- data_integrity(wine_data)
na_num_cols <- di$results$vars_num_with_NA$variable

df_na_rm <- limited_countries_df %>% mutate_at(vars(na_num_cols), ~replace_na(.,mean(., na.rm = TRUE)))


coord_plot(df_na_rm, group_var = "Country", group_func = function(x) mean(x, na.rm=TRUE))
```

The variable that the values are grouped by has to be categorical. The
generated plot could be pretty informative. It gives much more insight
when the target value is categorical.

Scaling options are insufficient because, in some cases, non-intuitive
and erroneous conclusions can be drawn from this chart - `0` in `Rating`
column should not represent the actual minimum of the variable, which is
`3`.

```{r}
plotar(wine_data, input = "price", target = "Rating", plot_type = "histdens")
```

Plotar works for categorical target only.

#### Scatter plots

```{r}
print(":(")
```

#### Contigency tables

```{r}
print(":(")
```

#### Other stats. (factor)

```{r}
desc_groups(limited_countries_df, group_var = "Country", group_func = median) %>%
  mutate(Country = fct_reorder(Country, desc(-Rating))) %>%  ggplot(aes(y=Country, x=Rating)) + geom_bar(stat = "identity") + 
  labs(title = "Average wine rating from different countries") 
  #coord_cartesian(xlim = c(3, 5)) 
```

Aggregates every numerical column by the function passed as a parameter
`group_func`; groups are selected based on the parameter `group_var`

```{r}
desc_groups_rank(limited_countries_df, group_var = "Country")
```

Describes how averages from every category (specified in `group_var`
parameter) are ranked. Behaves similarly to the `desc_group` function.

`group_var` has to be categorical.

### Multivar.

#### PCA

```{r}

 data_integrity_model(data=wine_data, model_name="pca")

```

Provides only a suggestion of which columns contain invalid types or
missing data to use a certain model - one of which could be PCA.

#### Stat. models

```{r}
print(":(")
```

The only function connected anyhow to statistical models in the given
package is `data_integrity_model` which provides some information on
which variables should be transformed in order to use the chosen model
on the dataset.

When it comes to binary target, there are some functions providing some
more advanced calculations, for instance `gain_lift` that plots the
*gain curve* and the lift chart. A little bit more information about the
methodology and usage of this function can be found here:
<https://livebook.datascienceheroes.com/model-performance.html#scoring_data>

#### PCP

```{r}
print(":(")
```

### Transform.

#### Imputation

```{r}
print(":(")
```

#### Scaling

```{r}
new_sweetness <- range01(wine_data$sweetness)

head(new_sweetness, 3)

```

Scales one selected variable into the [0, 1] range. Removes all `NA`
values - those are not taken into account.

It could take more parameters and scale multiple variables at once.

#### Skewness

```{r}
print(":(")
```

#### Outlier treatment

```{r}
data_prep = prep_outliers(data = wine_data, input = c('price','num_review'), method = "tukey", type='stop')

print(paste0("Min price in the original dataset: ", min(wine_data$price), ", max price: ", max(wine_data$price)))
print(paste0("Min price in the prep dataset: ", min(data_prep$price), ", max price: ", max(data_prep$price)))

```

Outlier treatment is done using functions defining the outlier
threshold - `tukey`, `hampel` or `bottom_top` method. Function
`prep_outliers`, imputes the outliers based on the method and threshold.
The imputation methods are simple - `stop` replaces outliers with the
threshold values and `set_na` replaces them with `NA`.

#### Binning

```{r}
bins_wine_data <- discretize_get_bins(wine_data, n_bins=5)
binned_wine_data <- discretize_df(wine_data, bins_wine_data)

freq(binned_wine_data$price)
```

The package provides some robust functions capable of binning numerical
variables.

The workflow of converting numerical columns into categorical is
following. Firstly intervals into which the selected variables will be
divided are generated. This can be done using the function
`discretize_get_bins` which returns selected variable names and
intervals separated with `|` sign.

Later, the `discretize_df` function can be used, which returns a
dataframe with column data converted according to the results of the
previous function.

All of this can be also done with the wrapper function
`convert_df_to_categoric`, which combines the operations of the function
described above.

Another way of binning provided by the package is using the function
`discretize_rgr`, which discretizes the given numeric vector by
maximizing the gain ratio between each bucket and the target variable.
Unfortunately, the function supports the categorical target variables.

#### Merging levels

```{r}
print(":(")
```

### Reporting

#### Reports

```{r}
print(":(")
```

The package doesn't provide any kind of summary or report containing
grouped information.

#### Saving outputs

```{r}

plt <- coord_plot(df_na_rm, group_var = "Country", group_func = function(x) mean(x, na.rm=TRUE), print_table = FALSE)

plt <- plot(sin, -pi, 2*pi)

export_plot(plt, path_out = ".", file_name = "plot.jpg")

```

All of the generated plots can be saved into the file.

Saving different types of outputs is not supported by the package, but
it turns out exporting plot is not well handled. I couldn't produce any
satisfying results with plotting functions from the package.

Some of the plot functions that are in the package have also an option
to automatically export the plot image.

### General description and opinion

To sum up, the package `funModeling` offers some great solutions, but
there is a lot of room for improvement in this package - below are some
of the most significant observations that I made during the
investigation of this package.

Pros:

-   descriptive summaries of multiple variables: `data_integrity`,
    `status` and `var_rank_info` - plotting functions `freq`, `plotar`
    and `coord_plot`

-   bivariate descriptions connected to the information theory

-   binning functions are fine but could be more diversified

-   does not reinvent the wheel, recreating well known functions from
    different packages

Cons:

-   non-uniform and unintuitive function naming - why plotting functions
    are named `plotar`, `coord_plot` and `freq` or `gain_lift`

-   non-uniform parameters - some functions have more parameters whilst
    the others don't, even though they could - missing option to export
    plot for `coord_plot`

-   unintuitive outputs - some functions primarily are meant to plot
    with an option to produce a numerical summary, but the primarily
    function of the others is to return the summary and have an option
    to plot the output - many functions supports only binary target

-   lack of documentation and representative examples - plots may be too
    colourful, different fill style doesn't carry any information

-   uses deprecated method (from `dplyr` or `ggplot2`)

The package `funModeling` is meant to be a representative example of
data preparation and other stages of predictive modeling as written in
the package description: *Around 10% of almost any predictive modeling
project is spent in predictive modeling, 'funModeling' and the book Data
Science Live Book (<https://livebook.datascienceheroes.com/>) is
intended to cover the remaining 90%: data preparation, profiling,
selecting best variables 'dataViz', assessing model performance and
other functions.*

However, neither the book nor the package delivers what it promises
since many topics and examples are very briefly described, and some
functions seems to be unfinished. But all in all, as I mentioned before,
both the package has some interesting features and the book contains a
few better chapters.

## Summary

| Task type  | Task                  | Yes/No |
|:----------:|-----------------------|--------|
|  Dataset   | Variable types        | Yes    |
|            | Dimensions            | No     |
|            | Other info            | Yes    |
|            | Compare datasets      | Yes    |
|  Validity  | Missing values        | Yes    |
|            | Redundant col.        | No     |
|            | Outliers              | Yes    |
|            | Atypical values       | No     |
|            | Level encoding        | No     |
|  Univar.   | Descriptive stat.     | Yes    |
|            | Histograms            | Yes    |
|            | Other dist. plots     | No     |
|            | Bar plots             | Yes    |
|            | QQ plots              | No     |
|   Bivar.   | Descriptive stat.     | Yes    |
|            | Correlation matrix    | No     |
|            | 1 vs each corr.       | Yes    |
|            | Time-dependency       | No     |
|            | Bar plots by target   | Yes    |
|            | Num. plots by target  | Yes    |
|            | Scatter plots         | No     |
|            | Contigency tables     | No     |
|            | Other stats. (factor) | No     |
| Multivar.  | PCA                   | No     |
|            | Stat. models          | No     |
|            | PCP                   | No     |
| Transform. | Imputation            | No     |
|            | Scaling               | Yes    |
|            | Skewness              | No     |
|            | Outlier treatment     | Yes    |
|            | Binning               | Yes    |
|            | Merging levels        | No     |
| Reporting  | Reports               | No     |
|            | Saving outputs        | No     |
