---
title: "Projekt 1.2"
author: "Imię Nazwisko"
date: '`r Sys.Date()`'
output: html_document
---

# Pakiet: nazwa_pakietu
# Zadanie: klasyfikacja/regresja


```{r}
#tutaj ładuje wszystkie potrzebne biblioteki
#library()

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview of functionalities

### Dataset

```{r}

```

#### Variable types

```{r}

```

#### Dimensions

```{r}

```

#### Other info

```{r}

```

#### Compare datasets

```{r}

```

### Validity

#### Missing values 

```{r}

```

#### Redundant col.

```{r}

```

#### Outliers 

```{r}

```


#### Atypical values

```{r}

```


#### Level encoding 

```{r}

```

### Univar.

#### Descriptive stat.

```{r}

```

#### Histograms 

```{r}

```

#### Other dist. plots

```{r}

```

#### Bar plots 

```{r}

```

#### QQ plots

```{r}

```

### Bivar.     

#### Descriptive stat.

```{r}

```

#### Correlation matrix 

```{r}

```

#### 1 vs each corr.   

```{r}

```

#### Time-dependency  

```{r}

```

#### Bar plots by target  

```{r}

```

#### Num. plots by target 

```{r}

```

#### Scatter plots 

```{r}

```

#### Contigency tables   

```{r}

```

#### Other stats. (factor)

```{r}

```


### Multivar.  

#### PCA 

```{r}

```

#### Stat. models  

```{r}

```

#### PCP        

```{r}

```


### Transform. 

#### Imputation

```{r}

```

#### Scaling 

```{r}

```

#### Skewness   

```{r}

```

#### Outlier treatment  

```{r}

```

#### Binning  

```{r}

```

#### Merging levels     

```{r}

```

### Reporting  

#### Reports

```{r}

```

#### Saving outputs        

```{r}

```



## Summary

|  Task type | Task                  | Yes/No |
|:----------:|-----------------------|--------|
|   Dataset  | Variable types        |        |
|            | Dimensions            |        |
|            | Other info            |        |
|            | Compare datasets      |        |
|  Validity  | Missing values        |        |
|            | Redundant col.        |        |
|            | Outliers              |        |
|            | Atypical values       |        |
|            | Level encoding        |        |
|   Univar.  | Descriptive stat.     |        |
|            | Histograms            |        |
|            | Other dist. plots     |        |
|            | Bar plots             |        |
|            | QQ plots              |        |      
|   Bivar.   | Descriptive stat.     |        |       
|            | Correlation matrix    |        |
|            | 1 vs each corr.       |        |
|            | Time-dependency       |        |             
|            | Bar plots by target   |        |
|            | Num. plots by target  |        |
|            | Scatter plots         |        |
|            | Contigency tables     |        |
|            | Other stats. (factor) |        |
|  Multivar. | PCA                   |        |      
|            | Stat. models          |        |
|            | PCP                   |        |
| Transform. | Imputation            |        |
|            | Scaling               |        |
|            | Skewness              |        |
|            | Outlier treatment     |        |
|            | Binning               |        |
|            | Merging levels        |        |
|  Reporting | Reports               |        |
|            | Saving outputs        |        |  
