---
title: "Projekt 1.2"
author: "Grzegorz Pióro"
date: '`r Sys.Date()`'
output: html_document
---

# Pakiet: smartEDA
# Zadanie: klasyfikacja


```{r,warning=FALSE,message=FALSE}
#tutaj ładuje wszystkie potrzebne biblioteki
dane <- read.csv('gender_classification_v7.csv',header = TRUE)
library(SmartEDA)
library(dplyr)
library(ggplot2)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview of functionalities

### Dataset

This dataset contains 7 features and a label column.

long_hair - This column contains 0's and 1's where 1 is "long hair" and 0 is "not long hair".
forehead_width_cm - This column is in CM's. This is the width of the forehead.
forehead_height_cm - This is the height of the forehead and it's in Cm's.
nose_wide - This column contains 0's and 1's where 1 is "wide nose" and 0 is "not wide nose".
nose_long - This column contains 0's and 1's where 1 is "Long nose" and 0 is "not long nose".
lips_thin - This column contains 0's and 1's where 1 represents the "thin lips" while 0 is "Not thin lips".
distance_nose_to_lip_long - This column contains 0's and 1's where 1 represents the "long distance between nose and lips" while 0 is "short distance between nose and lips".

```{r}
print(head(dane))
```


#### Variable types

```{r}
ExpData(data = dane, type = 1)[3:9,]
```

#### Dimensions

```{r}
ExpData(data = dane, type = 1)[1:2,]
```

#### Other info

You can add your own functions to summarise data as well.

```{r}
quantile_10 = function(x){
  quantile_10 = quantile(x, na.rm = TRUE, 0.1)
}
ExpData(data=dane, type=2, fun=c("quantile_10"))
```

#### Compare datasets

There is no function for this

### Validity

#### Missing values 

```{r}
ExpData(data=dane,type = 2)
```

#### Redundant col.

No such function found.

#### Outliers 

```{r}
ExpOutliers(dane, varlist = c("forehead_width_cm","forehead_height_cm","nose_wide"), method = "boxplot",  treatment = "mean", capping = c(0.1, 0.9))
```
```{r}
ExpOutliers(dane, varlist = c("forehead_width_cm","forehead_height_cm","nose_wide"), method = "3xStDev",  treatment = "median", capping = c(0.1, 0.9))
```

#### Atypical values

Unfortunately, there isn't such a function in the package description.


#### Level encoding 

Unfortunately, there isn't such a function in the package description.

### Univar.

#### Descriptive stat.

```{r}
ExpCTable(dane,Target=NULL,margin=1,clim=10,nlim=3,round=2,bin=NULL,per=T)
```

#### Histograms 

Unfortunately, there isn't such a function in the package description.

#### Other dist. plots

```{r}
ExpNumViz(dane,target=NULL,nlim=10,Page=c(2,1),sample=2)
```

#### Bar plots 

```{r}
ExpCatViz(dane,target=NULL,col ="slateblue4",clim=10,margin=2,Page = c(2,2),sample=4)
```

#### QQ plots

```{r}
qqp <- ExpOutQQ(dane,nlim=10,fname=NULL,Page=c(2,2),sample=4)
qqp[[1]]
```

### Bivar.     

#### Descriptive stat.

```{r}
ExpNumStat(dane,by="GA",gp="gender",Qnt=seq(0,1,0.1),MesofShape=2,Outlier=TRUE,round=2)
```

#### Correlation matrix 

```{r}
```

#### 1 vs each corr.   

```{r}
```

#### Time-dependency  

```{r}
```

#### Bar plots by target  

```{r}
ExpCatViz(dane, margin = 2, target = "gender", 
          col = c("red","green"))
```

#### Num. plots by target 

```{r}
ExpNumViz(dane,target="gender",type=1,nlim=3,fname=NULL,col=c("darkgreen","springgreen3","springgreen1"),Page=c(2,1),sample=2)
```

#### Scatter plots 

```{r}
ExpNumViz(dane, scatter = TRUE)
```

#### Contigency tables   

```{r}
```

#### Other stats. (factor)

```{r}
ExpParcoord(dane,Group="nose_long",Stsize=NULL,Nvar=c("long_hair","forehead_width_cm","forehead_height_cm","nose_wide","nose_long","lips_thin","distance_nose_to_lip_long","gender"))

ExpKurtosis(dane$forehead_width_cm,type = 'moment')
```


### Multivar.  

#### PCA 

```{r}
```

#### Stat. models  

```{r}
```

#### PCP        

```{r}
```


### Transform. 

#### Imputation

```{r}
```

#### Scaling 

```{r}
```

#### Skewness   

```{r}
ExpSkew(dane, type = 'moment')
```

#### Outlier treatment  

```{r}
```

#### Binning  

```{r}
```

#### Merging levels     

```{r}
```

### Reporting  

#### Reports

```{r}
#ExpReport(dane,Target="gender",theme="Default",op_file="Samp2.html")
```

#### Saving outputs        

```{r}
```



## Summary

|  Task type | Task                  | Yes/No |
|:----------:|-----------------------|--------|
|   Dataset  | Variable types        |    Yes    |
|            | Dimensions            |    Yes    |
|            | Other info            |    Yes    |
|            | Compare datasets      |    No    |
|  Validity  | Missing values        |    Yes    |
|            | Redundant col.        |    No    |
|            | Outliers              |    Yes    |
|            | Atypical values       |    No    |
|            | Level encoding        |    No    |
|   Univar.  | Descriptive stat.     |    Yes    |
|            | Histograms            |    No    |
|            | Other dist. plots     |    Yes    |
|            | Bar plots             |    Yes    |
|            | QQ plots              |    Yes    |      
|   Bivar.   | Descriptive stat.     |    Yes    |       
|            | Correlation matrix    |    No    |
|            | 1 vs each corr.       |    No    |
|            | Time-dependency       |    No    |             
|            | Bar plots by target   |    Yes    |
|            | Num. plots by target  |    Yes    |
|            | Scatter plots         |    Yes    |
|            | Contigency tables     |    No    |
|            | Other stats. (factor) |    Yes    |
|  Multivar. | PCA                   |    No    |      
|            | Stat. models          |    No    |
|            | PCP                   |    No    |
| Transform. | Imputation            |    No    |
|            | Scaling               |    No    |
|            | Skewness              |    Yes    |
|            | Outlier treatment     |    No    |
|            | Binning               |    No    |
|            | Merging levels        |    No    |
|  Reporting | Reports               |    Yes    |
|            | Saving outputs        |    No    |  