---
title: "Projekt 1.2"
author: "Weronika Dyszkiewicz"
date: '`r Sys.Date()`'
output: html_document
---

# Pakiet: summarytools
# Zadanie: klasyfikacja


```{r}
#tutaj ładuje wszystkie potrzebne biblioteki
library('summarytools')
loan_approval <- read.csv('loan_sanction_train.csv')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview of functionalities

### Dataset

```{r}

```

#### Variable types

```{r}
print(dfSummary(loan_approval), method = "render")

```

As can be seen in the output above, the type of variable is shown along with the variable name. This is followed by basic descriptive statistics for numeric variables or the values for categorical variables. A simple histogram or bar chart is plotted showing the distribution of the variable. Overall, it provides you with a concise summary of the variables in the data.

#### Dimensions
In the function dfSummary, we can see a dimension of dataset but the package offers also the alternative:

```{r}
what.is(loan_approval)
```
An alternative to calling in turn class, typeof, dim, and so on. A call to this function will readily give all this information at once.

#### Other info
dfSummary() is the function that provide summary of a data frame consisting of: variable names and types, labels if any, factor levels, frequencies and/or numerical summary statistics, barplots/histograms, and valid/missing observation counts and proportions. what.is() function returns the combination of most common “macro-level” functions that describe an object.
To obtain more detailed statistics on numeric variables, we can use the descr function.

```{r}
descr(loan_approval$ApplicantIncome)
```

freq function is most useful for categorical variables.

```{r}

freq(loan_approval$Education)

```
ctable is used to cross-tabulate frequencies for a pair of categorical variables.
```{r}
print(
  ctable(loan_approval$Education, loan_approval$Gender),
  method = "render"
)
```
#### Compare datasets
function not found

### Validity
freq() and dfSummary functions used above.

#### Missing values 
freq() and dfSummary functions used above.
We can set to FALSE in report.nas argument to turn off reporting of missing values. 

#### Redundant col.

function not found

#### Outliers 

function not found

#### Atypical values

function not found

#### Level encoding 

function not found

### Univar.

#### Descriptive stat.
descr - all common univariate descriptive stats applied to a single vector or to all numerical vectors
contained in a data frame.

```{r}
descr(loan_approval$ApplicantIncome)
```

#### Histograms 

dfSummary function can display histograms column
(printed above)

#### Other dist. plots
function not found

#### Bar plots 
dfSummary function can display barplots column
(printed above)

#### QQ plots

function not found


### Bivar.     

#### Descriptive stat.

function not found

#### Correlation matrix 

function not found

#### 1 vs each corr.   

function not found

#### Time-dependency  

function not found

#### Bar plots by target  

function not found

#### Num. plots by target 

function not found

#### Scatter plots 

function not found

#### Contigency tables   

function not found

#### Other stats. (factor)

function not found


### Multivar.  

#### PCA 

function not found

#### Stat. models  

function not found

#### PCP        

function not found

### Transform. 

#### Imputation

maybe: define_keywords Modify Keywords Used In Outputs

#### Scaling 

function not found

#### Skewness   
row name in descr():

```{r}
descr(loan_approval$LoanAmount)
```

#### Outlier treatment  

function not found

#### Binning  

function not found


#### Merging levels     
function not found


### Reporting  

#### Reports

Using the file argument with print() or view() / stview(), we can write outputs to a file, be it html, Rmd, md, or just plain text (txt). The file extension is used by the package to determine the type of content to write out

```{r}
#print(dfSummary(loan_approval), file = '~/summary_tools.Rmd')

```

#### Saving outputs        

Using the file argument with print() or view() / stview(), we can write outputs to a file, be it html, Rmd, md, or just plain text (txt). The file extension is used by the package to determine the type of content to write out.

```{r}
#view(dfSummary(loan_approval), file = '~/summary_tools.Rmd')
```

## Sources:
-https://cran.r-project.org/web/packages/summarytools/summarytools.pdf \
-https://cran.r-project.org/web/packages/summarytools/vignettes/introduction.html#data-frame-summaries-dfsummary \
-https://www.r-bloggers.com/2019/05/easily-explore-your-data-using-the-summarytools-package/

## Summary

|  Task type | Task                  | Yes/No   |
|:----------:|-----------------------|----------|
|   Dataset  | Variable types        |Yes       |
|            | Dimensions            |Yes       |
|            | Other info            |Yes       |
|            | Compare datasets      |No        |
|  Validity  | Missing values        |Yes       |
|            | Redundant col.        |No        |
|            | Outliers              |No        |
|            | Atypical values       |No        |
|            | Level encoding        |No        |
|   Univar.  | Descriptive stat.     |Yes       |
|            | Histograms            |Yes       |
|            | Other dist. plots     |No        |
|            | Bar plots             |Yes       |
|            | QQ plots              |No        |      
|   Bivar.   | Descriptive stat.     |No        |       
|            | Correlation matrix    |No        |
|            | 1 vs each corr.       |No        |
|            | Time-dependency       |No        |             
|            | Bar plots by target   |No        |
|            | Num. plots by target  |No        |
|            | Scatter plots         |No        |
|            | Contigency tables     |No        |
|            | Other stats. (factor) |No        |
|  Multivar. | PCA                   |No        |      
|            | Stat. models          |No        |
|            | PCP                   |No        |
| Transform. | Imputation            |Yes       |
|            | Scaling               |No        |
|            | Skewness              |Yes       |
|            | Outlier treatment     |No        |
|            | Binning               |No        |
|            | Merging levels        |No        |
|  Reporting | Reports               |Yes       |
|            | Saving outputs        |Yes       |  
