---
title: "Projekt 1.2"
author: "Laura Hoang"
date: '`r Sys.Date()`'
output: html_document
---

# Pakiet: visdat
# Zadanie: classification

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# libraries
library("visdat")
library("plotly")
```

## What does visdat do?
Initially inspired by [`csv-fingerprint`](https://github.com/setosa/csv-fingerprint),
`vis_dat` helps with visualising a dataframe and "get a look at the data" by displaying the
variable classes in a dataframe as a plot with `vis_dat`, and getting a brief
look into missing data patterns using `vis_miss`. `visdat` is a very simple
library containing only 6 functions.

## Overview of functionalities

### Dataset
This is a set of data created for rice classification. I recommend using this
dataset for educational purposes, for practice and to acquire the necessary
knowledge. It is modified dataset from this resource: link Jasmine - 1, Gonen - 0.

The dataset comes from:
<https://www.kaggle.com/datasets/mssmartypants/rice-type-classification>

```{r}
df <- read.csv2('data/riceClassification.csv', sep=',')
df[, c(3:5,7,8:11)] <- sapply(df[, c(3:5,7,8:11)], as.numeric)

print(head(df))

```

#### Variable types
`vis_dat()` visualises a dataframe showing you what the classes of the columns
are, and also displaying the missing data.

```{r}
vis_dat(df, sort_type = FALSE)

```

#### Dimensions
Package has no function for this property.

#### Other info
`vis_expect()` visualise where certain conditions hold true in your data.

```{r}
vis_expect(df, ~.x >= 25) 

```

#### Compare datasets
`vis_compare()` visualise differences between two dataframes of the same dimensions.

```{r}
a <- df[sample(nrow(df), 100), ]
b <- df[sample(nrow(df), 100), ]

vis_compare(a,b)

```

### Validity

#### Missing values 
`vis_miss()` visualises just the missing data, and allows for missingness to be clustered and columns rearranged.

```{r}
vis_miss(df)

```

In order to check the function, NA values were artificially added to the copy of data.
```{r}
df2 <- df
df2[sample(nrow(df2), 150), c(sample(ncol(df2), 10))] <- NA
df2[sample(nrow(df2), 100), c(sample(ncol(df2), 5))] <- NA
df2[sample(nrow(df2), 1000), c(sample(ncol(df2), 2))] <- NA
df2[sample(nrow(df2), 100), c(sample(ncol(df2), 8))] <- NA

vis_miss(df2)

```


#### Redundant col.
Package has no function for this property.

#### Outliers 
Package has no function for this property.


#### Atypical values
Package has no function for this property.


#### Level encoding 
Package has no function for this property.

### Univar.

#### Descriptive stat.
Package has no function for this property.

#### Histograms 
Package has no function for this property.

#### Other dist. plots
Package has no function for this property.

#### Bar plots 
Package has no function for this property.

#### QQ plots
Package has no function for this property.

### Bivar.     

#### Descriptive stat.
Package has no function for this property.

#### Correlation matrix 
`vis_cor()` visualise the correlation of variables in a nice heatmap.

```{r}
vis_cor(df)
```

#### 1 vs each corr.   
Package has no function for this property.

#### Time-dependency  
Package has no function for this property.

#### Bar plots by target  
Package has no function for this property.

The `vis_dat()` function however, has a `facet` argument, so there is a possibility to create small multiples of a similar plot for a level of a variable.
```{r}
vis_dat(df, facet = Class)
```

#### Num. plots by target 
Package has no function for this property.

#### Scatter plots 
Package has no function for this property.

#### Contigency tables   
Package has no function for this property.

#### Other stats. (factor)
Package has no function for this property.


### Multivar.  

#### PCA 
Package has no function for this property.

#### Stat. models  
Package has no function for this property.

#### PCP        
Package has no function for this property.


### Transform. 

#### Imputation
Package has no function for this property.

#### Scaling 
`vis_value()` visualise the value class of each cell in your data.
```{r}
vis_value(df)

```

#### Skewness   
Package has no function for this property.

#### Outlier treatment  
Package has no function for this property.

#### Binning  
Package has no function for this property.

#### Merging levels     
Package has no function for this property.

### Reporting  

#### Reports
Package has no function for this property.

#### Saving outputs
There is a possibility to make plots in visdat by wrapping them in plotly::ggplotly. Then, obtained graph can be saved / exported.
```{r}
# plot <- ggplotly(vis_dat(df))
# htmlwidgets::saveWidget(plot, "plot.html")
```

## Summary

|  Task type | Task                  | Yes/No |
|:----------:|:---------------------:|:------:|
|   Dataset  | Variable types        |   Yes  |
|            | Dimensions            |   No   |
|            | Other info            |   Yes  |
|            | Compare datasets      |   Yes  |
|  Validity  | Missing values        |   Yes  |
|            | Redundant col.        |   No   |
|            | Outliers              |   No   |
|            | Atypical values       |   No   |
|            | Level encoding        |   No   |
|   Univar.  | Descriptive stat.     |   No   |
|            | Histograms            |   No   |
|            | Other dist. plots     |   No   |
|            | Bar plots             |   No   |
|            | QQ plots              |   No   |      
|   Bivar.   | Descriptive stat.     |   No   |       
|            | Correlation matrix    |   Yes  |
|            | 1 vs each corr.       |   No   |
|            | Time-dependency       |   No   |             
|            | Bar plots by target   |   No   |
|            | Num. plots by target  |   No   |
|            | Scatter plots         |   No   |
|            | Contigency tables     |   No   |
|            | Other stats. (factor) |   No   |
|  Multivar. | PCA                   |   No   |      
|            | Stat. models          |   No   |
|            | PCP                   |   No   |
| Transform. | Imputation            |   No   |
|            | Scaling               |   Yes  |
|            | Skewness              |   No   |
|            | Outlier treatment     |   No   |
|            | Binning               |   No   |
|            | Merging levels        |   No   |
|  Reporting | Reports               |   No   |
|            | Saving outputs        |   Yes  |
