---
title: "Projekt 1.2"
author: "Malwina  Wojewoda"
date: '`r Sys.Date()`'
output: html_document
---

# Package: visdat

# Task: regression

```{r}
library("visdat")

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package description
Visdat allows for quick display of basic information about the data, such as missing values, variable distribution, variable correlations, and more. The visualizations generated by the package are interactive, which enables interactive filtering of data and anomaly detection.


## Overview of functionalities

### Dataset

The Bike Sharing Dataset is a collection of data on bike-sharing systems in the Capital Bikeshare program in Washington, D.C. The dataset contains 17,379 instances, each corresponding to a single hour of the day and a particular day from 2011 to 2012. The data were collected from both public and private sources and include information on weather conditions, holidays, and other factors that may influence bike usage. The target variable in this dataset is the total count of bike rentals. 

The dataset comes from: https://www.kaggle.com/datasets/ayessa/bike-sharing-dataset-regression?select=day.csv 
```{r}
df <- read.csv('regression_bike_rental.csv')
print(head(df))
```

#### Variable types
vis_dat() visualises a dataframe showing you what the classes of the columns are, and also displaying the missing data.
```{r}
vis_dat(df)
```
vis_guess() function infers the data type of each variable in a data frame and displays the results as a table.
```{r}
vis_guess(df)
```

#### Dimensions
The visdat package does not provide a function to display the dimensions of a data frame directly.


#### Other info
vis_expect() visualises certain conditions or values in your data. It takes two arguments: the data frame to be visualized and a list of expected values or patterns.
For example you can see if there are times where the values in your data are greater than or equal to 5
```{r}
vis_expect(df, ~.x >= 5)
```
vis_value() function is used to visualize the unique values and their frequencies for each variable in a data frame. It works only on numeric data.
```{r}
vis_value(dplyr::select(df, where(is.numeric)))

```
vis_binary() visualise the occurrence of binary values in your data.
```{r}
binary_cols <- apply(df, 2, function(x) {
  all(x %in% c(0, 1, NA) | is.na(x))
})
binary_df <- df[, binary_cols]
vis_binary(binary_df)
```
#### Compare datasets
vis_compare() visualise differences between two dataframes of the same dimensions.
```{r}
df1 <- df[c(1:200), ]
df2 <- df[c(201:400), ]
vis_compare(df1, df2)
```

### Validity

#### Missing values
vis_miss() visualises just the missing data, and allows for missingness to be clustered and columns rearranged.

In order to check the function, NA values were artificially added to the copy of data.
```{r}
df_with_missing_values <- df
df_with_missing_values[c(100:200), 2] <- NA
df_with_missing_values[c(500:530), 4] <- NA
df_with_missing_values[c(300:600), 8] <- NA
vis_miss(df_with_missing_values)
```
Besides, vis_dat() visualises a dataframe showing you what the classes of the columns are, and also displaying the missing data.
```{r}
vis_dat(df_with_missing_values)
```

#### Redundant col.
Package does not have a function that explicitly specifies that columns are redundant.

#### Outliers
The package does not support this functionality.


#### Atypical values
The package does not support this functionality.

#### Level encoding
The package does not support this functionality.

### Univar.

#### Descriptive stat.
The package does not support this functionality.

#### Histograms
The package does not support this functionality.

#### Other dist. plots
The package does not support this functionality.

#### Bar plots
The package does not support this functionality.

#### QQ plots
The package does not support this functionality.

### Bivar.

#### Descriptive stat.
The package does not support this functionality.

#### Correlation matrix
`vis_cor()` visualise the correlation of variables in a heatmap.
```{r}
vis_cor(dplyr::select(df, where(is.numeric)))
```

#### 1 vs each corr.
The package does not support this functionality.

#### Time-dependency
The package does not support this functionality.

#### Bar plots by target
The package does not support this functionality.

#### Num. plots by target
The package does not support this functionality.

#### Scatter plots
The package does not support this functionality.

#### Contigency tables
The package does not support this functionality.

#### Other stats. (factor)
The package does not support this functionality.

### Multivar.

#### PCA
The package does not support this functionality.

#### Stat. models
The package does not support this functionality.

#### PCP
The package does not support this functionality.

### Transform.

#### Imputation
The package does not support this functionality.

#### Scaling
The package does not support this functionality.

#### Skewness
The package does not support this functionality.

#### Outlier treatment
The package does not support this functionality.

#### Binning
The package does not support this functionality.

#### Merging levels
The package does not support this functionality.

### Reporting

#### Reports
The package does not support this functionality.

#### Saving outputs
The package does not support this functionality.

## Summary

| Task type  | Task                  | Yes/No |
|:----------:|-----------------------|--------|
|  Dataset   | Variable types        |  Yes   |
|            | Dimensions            |  No    |
|            | Other info            |  Yes   |
|            | Compare datasets      |  Yes   |
|  Validity  | Missing values        |  Yes   |
|            | Redundant col.        |  No    |
|            | Outliers              |  No    |
|            | Atypical values       |  No    |
|            | Level encoding        |  No    |
|  Univar.   | Descriptive stat.     |  No    |
|            | Histograms            |  No    |
|            | Other dist. plots     |  No    |
|            | Bar plots             |  No    |
|            | QQ plots              |  No    |
|   Bivar.   | Descriptive stat.     |  No    |
|            | Correlation matrix    |  Yes   |
|            | 1 vs each corr.       |  No    |
|            | Time-dependency       |  No    |
|            | Bar plots by target   |  No    |
|            | Num. plots by target  |  No    |
|            | Scatter plots         |  No    |
|            | Contigency tables     |  No    |
|            | Other stats. (factor) |  No    |
| Multivar.  | PCA                   |  No    |
|            | Stat. models          |  No    |
|            | PCP                   |  No    |
| Transform. | Imputation            |  No    |
|            | Scaling               |  No    |
|            | Skewness              |  No    |
|            | Outlier treatment     |  No    |
|            | Binning               |  No    |
|            | Merging levels        |  No    |
| Reporting  | Reports               |  No    |
|            | Saving outputs        |  No    |
